# SWS Resources {#resources }

This section enclose a detailed description of all the auxiliary resources needed by the modules to accomplish their calculation. It includes definition of code lists, used to define the various dimensions of data sets, and data tables. 

## Code Lists

Code lists describe the dimentions that compose the different datasets, they are designed by the users to store analytical results from SWS modules. Each dataset have a set of codes and their associated description, thus Codelists are used within different sets for the sake of standardization, visualization and metadata associated to each dimentions. \
The code lists that describe `Value of Agricultural Production ` dataset are the following : 

  -  `GeographicAreaM49` :  Represent the spatial scale, it is composed by countries territories, , regional aggregates, regional special groups aggregates, global aggregates. 
  
  -  `measuredElement ` : Represent the different element calculated by the plugin through the methodology metioned above. For instance Gross production in different currencies and Gross Production index numbers. 
  
  -   `measuredItemCPC ` : Those items wants to take measure of production. For example, commodities and commodity groups produced by a country;
  
  -  `timePointYears` : The time unit (year) data is displayed for.

<br>

## Data Tables {#datatables}

Datatables are flexible tool made available inside the Statistical Working System to store a wide range of usefull information. They indeed provide a strong support to R module to record countries and items groups composition, to map conversion factors and to store different type of data. 
Variable names (column names) of datatables are more flexible compared to those of datasets, they can accommodate all kind of names and are not strictly constrained by code lists or by the domain in which they are stored.
Below a detailed description of all the datatable used in the Value of Production module. 

<br>

### Base Year Parameter

  * **Datatable :** `Value of Production - Base Year Parameter`
  * **Domain :** `Agriculture Production` 
  * **Usage :** Used to define the base year. The plugin will calculate the three-year base period around the specified value. 
  
  <br>

```{r echo=FALSE}
name = c("Base Year")

desc = c("Base Year of the Value of Agricultural Plugin")


knitr::kable(data.frame(Field= name, Description= desc ) , caption = "Input parameter for the base year range.", col.names = c("Field", "Description") )

```

<br>


### Supplementary International Dollar

  * **Datatable :** `Supplementary International Dollar`
  * **Domain :** `Agriculture Production` 
  * **Usage :** Used to import International Dollar from FAOSTAT to SWS for validation procedure.
  
  <br>

```{r echo=FALSE}
name = c(
"Domain Code",
"Area Code (M49)",
"Area",
"Element Code",
"Element",
"Item Code",
"Item",
"Year",
"Unit",
"Value"
)

desc = c(
'Domain Code of the dissemination platform',
'Area Code M49',
'Area name',
'Element code for production',
'Element name [Int.$/tonnes]',
'FAOSTAT item code',
'Item name',
'Year selected',
'International Dollar/Tonnes',
'Price'
)


knitr::kable(data.frame(Field= name, Description= desc ) , caption = "International Dollar data field summary.", col.names = c("Field", "Description") )

```

<br>

### Value of Production - Country {#countrytab}

  * **Datatable :** `Value of Production - country`
  * **Domain :** `Agriculture Production` 
  * **Usage :** Used to define the countries for which the Value of Production is calculated.
  
  <br>

```{r echo=FALSE}
name = c(
"Country Code",
"Country",
"M49_code",
"ISO2_code",
"ISO3_code",
"Start Date",
"End Date"

)

desc = c(
'FAOSTAT country code',
'Name of the country',
'M49 country code',
'ISO2 country code',
'ISO3 country code',
'Starting validity of the country',
'Ending validity of the country'

)


knitr::kable(data.frame(Field= name, Description= desc ) , caption = "Country list field summary.", col.names = c("Field", "Description") )

```
<br>

### Value of Production - Country Group {#countrygrouptab}

  * **Datatable :** `Value of Production - Country Group`
  * **Domain :** `Agriculture Production` 
  * **Usage :** Used to define the countries groups for aggregations.
  
  <br>

```{r echo=FALSE}
name = c(
"Country group code",
"Country group",
"Country Code",
"Country",
"M49_code",
"ISO2_code",
"ISO3_code"

)

desc = c(
'FAOSTAT country group code',
'FAOSTAT country group name',
'FAOSTAT country code',
'Name of the country',
'M49 country code',
'ISO2 country code',
'ISO3 country code'

)


knitr::kable(data.frame(Field= name, Description= desc ) , caption = "Country group list field summary.", col.names = c("Field", "Description") )

```

<br>


### Value of Production - Item {#itemtab}

  * **Datatable :** `Value of Production - Item`
  * **Domain :** `Agriculture Production` 
  * **Usage :** Used to define the items list for which the Value of Production is calculated .
  
  <br>

```{r echo=FALSE}
name = c(
"Item Code",
"Item Name",
"Description",
"CPC code"
)

desc = c(
'FAOSTAT Item code',
'Name of the item',
'Description of the item',
'Corresponding CPC item code'
)


knitr::kable(data.frame(Field= name, Description= desc ) , caption = "Item list data field summary.", col.names = c("Field", "Description") )

```

<br>

### Value of Production - Item group {#itemgrouptab}

  * **Datatable :** `Value of Production - Item group`
  * **Domain :** `Agriculture Production`
  * **Usage :** Used to define the items group list for items aggregations .
  
  <br>

```{r echo=FALSE}
name = c(
"Item Group Code",
"Item Group",
"Item Code",
"Item Name",
"factor",
"CPC code"
)

desc = c(
'FAOSTAT Item group code',
'Name of the item group',
'FAOSTAT item code',
'Name of the item',
'Factor for item aggregation',
'Corresponding CPC item code'
)


knitr::kable(data.frame(Field= name, Description= desc ) , caption = "Item list data field summary.", col.names = c("Field", "Description") )

```


### Value of Production - LOG

  * **Datatable :** `Value of Production - LOG`
  * **Domain :** `Agriculture Production` 
  * **Usage :** Provide a LOG history of plugin runs.
  
  <br>

```{r echo=FALSE}
name = c("User",
         "Execution Date",
         "Base Year Parameter",
         "Item aggregation parameter",
         "Countries aggregation parameter",
         "Source Production data",
         "Source Prices data",
         "Lines writed",
         "Lines omitted",
         "Lines discarded"
         
)

desc = c("User email of the user that run the plugin",
         "Date of the execution",
         "Base year selected",
         "Item aggregation level",
         "Countries aggregation level",
         "Source of production data",
         "Source of Producer prices data",
         "Data points writed by the plugin",
         "Data points not updated by the plugin",
         "Datapoints not writed by the plugin"
         
)


knitr::kable(data.frame(Field= name, Description= desc ) , caption = "Item list data field summary.", col.names = c("Field", "Description") )

```
